Formalizing Stack Safety as a Security Property

### 2022-12-07 submission5/core.tex
Variants in formalism

For a given system, assume an equivalence class \(\sim\) on values.
Two states are variants with respect to a set of elements, \(\components\),
if they agree on the value of every element not in \(\components\) and
all of their values are equivalent under \(\sim\).
Our notion of non-interference involves comparing the traces of such
\(\components\)-variants. We use this to define sets of irrelevant elements,
and secrets in general.

\definition Machine states \(\mach\) and \(\nach\) are {\em \(\components\)-variants},
written \(\mach \approx_\components \nach\), if, for
all \(\component \not \in \components\), \(\mach[\component] = \nach[\component]\)
and for all \(\component\), \(\mach[\component] \sim \nach[\component]\).

>>>>

\definition For a given system, assume an equivalence relation \(\sim\) on values.
Machine states \(\mach\) and \(\nach\) are {\em \(\components\)-variants},
written \(\mach \approx_\components \nach\), if, for
all \(\component \not \in \components\), \(\mach[\component] = \nach[\component]\),
and for all \(\component \in \components\), \(\mach[\component] \sim \nach[\component]\).
